INTELLIGENT SYSTEMS

### 2021-04-18 papers/paper_9.tex
finish paper 9

>>>>

\subsubsection{Top1\&Top5 Precision Experiments Under Different Global Scopes}
Comparisons were also made on the two personal Top1 \& Top5 precision 
metrics. The results obtained by both methods are those shown in table \ref{T12}.
\begin{table}[h!]
    \centering
    \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|c|cc|cc|}
        \hline
        \multirow{2}{*}{Method} & \multicolumn{2}{c|}{LFW} & \multicolumn{2}{c|}{CASIA-WebFace}\\
        & Top5-acc & Top1-acc & Top5-acc & Top1-acc\\
        \hline
        v2 & 96.96 & 93.63 & 85.97 & 78.24\\
        \hline
        proposed & \bfseries{99.20} & \bfseries{98.86} & \bfseries{93.31} & \bfseries{84.92}\\
        \hline    
    \end{tabular}
    \end{adjustbox}
    \caption{Top1\&Top5 Precision (\%) between two methods.}
    \label{T12}
\end{table}

\subsubsection{Experiments On Similar Fase Dataset (SFD)}
In this experiment, the performance of another method called DeepID2+ \cite{0902694017} 
was also verified. The reference dataset in this case is just SFD. The experiment 
is conducted with images in which there are similar faces, divided by 
degrees. Also in this case accuracy and sensitivity are the metrics considered. 
In table \ref{SFDCompMeth} you can see the results obtained by all the models. As we 
can see, the lower the similarity level (towards grade 5), the higher the levels 
of accuracy and true positive rate achieved by the methods. The proposed 
method, however, managed to obtain the best performances also in this experiment. 
his Thighlights the importance of using external features that are 
not considered by the other methods.
\begin{table}[h!]
    \centering
    \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|c|ccccc|}
        \hline
        \multirow{2}{*}{Method} & \multicolumn{5}{c|}{Similar Face Dataset (SFD)}\\
        & \RN{1} & \RN{2} & \RN{3} & \RN{4} & \RN{5}\\
        \hline
        DeepID2+ acc. & 49.73 & 59.75 & 58.64 & 64.37 & 66.33\\
        DeepID2+ tpr. & 71.77 & 78.08 & 76.28 & 81.77 & 83.17\\
        \hline
        v2 acc. & 42.81 & 54.75 & 55.64 & 66.97 & 68.22\\
        v2 tpr. & 63.33 & 70.00 & 65.33 & 71.67 & 68.08\\
        \hline
        proposed acc. & \bfseries{78.29} & \bfseries{83.19} & \bfseries{82.19} & \bfseries{86.11} & \bfseries{86.40}\\
        proposed tpr. & \bfseries{79.17} & \bfseries{83.33} & \bfseries{79.67} & \bfseries{85.67} & \bfseries{84.67}\\
        \hline
    \end{tabular}
    \end{adjustbox}
    \caption{Comparison abount v2, DeepID+ and proposd methods on SFD dataset}
    \label{SFDCompMeth}
\end{table}

\subsubsection{Supplementary Experiment on SFD}
The last experiment is carried out only between the v2 method, which does 
not use external features, and the one proposed. The aim is to see which of 
the two can best distinguish the similarities of faces. The values shown in the 
image \ref{fig:fei} represent the L2 distance between the upper and lower image. It can 
be seen that for v2, in all three images, the same face always appears, while 
the proposed method, thanks to the combination of external and internal 
features, manages to distinguish both people.
\begin{figure}[h!]
    \centering
    \includegraphics[width = 0.8\linewidth]{images/paper9/features.png}
    \centering
    \caption{The importance of external and internal features.}
    \label{fig:fei}
\end{figure}

\subsection{CONCLUSION}
What appears strange is that the greater the similarity between two faces, 
the lower the recognition accuracy achieved by all the models. Even if the 
addition of external and internal features represent a benefit for the purpose 
of recognition, at the computation level this operation turns out to be expensive 
in the training phase even if it is lightened by the use of mini-batches 
(triple) and the various optimizations of the network.
